Visualising 3D structures

### 2022-03-16 analysis/ThreeDStructure.Rmd
workflowr:::wflow_publish(files = "analysis/ThreeDStructure.Rmd")

First, let's just load one of them 
```{r}
# the 'real' one from X-ray crystallography
ara_SOS3_real <- read.pdb('data/SOS3_OG0000189/Arabidopsis_SOS3_1v1f.pdb')
# the alphafold ones

amphibolis_SOS3_alpha <- read.pdb('data/SOS3_OG0000189/Amphibolis_fixed_SOS3_40588.result/Amphibolis_fixed_SOS3_40588_unrelaxed_rank_1_model_4.pdb')
posi_SOS3_alpha <- read.pdb('data/SOS3_OG0000189/6P_australis_SOS3_dcfd4.result/6P_australis_SOS3_dcfd4_unrelaxed_rank_1_model_1.pdb')
```

@@

```{r}

m_glimpse(posi_SOS3_alpha, outline = FALSE) %>% 
  m_spin()
```

```{r}
m1 <- r3dmol() %>%
  m_add_model(data = posi_SOS3_alpha, format = "pdb") %>%
  m_zoom_to()
m2 <- r3dmol() %>%
  m_add_model(data = amphibolis_SOS3_alpha, format = "pdb") %>%
  m_zoom_to()
m3 <- r3dmol() %>%
  m_add_model(data = '1v1f', format = "pdb") %>%
  m_zoom_to()
m_grid(
  viewer = list(m1, m2, m3),
  rows = 2,
  cols = 2,
  #control_all = TRUE,
  #viewer_config = m_viewer_spec(
  #  backgroundColor = "lightblue"
  #)
)
```

>>>>

First, let's just load one of them 
```{r}
# the 'real' one from X-ray crystallography
ara_SOS3_real <- read.pdb('data//SOS3_OG0000189/Arabidopsis_SOS3_1v1f.pdb')
# the alphafold ones

amphibolis_SOS3_alpha <- read.pdb('data//SOS3_OG0000189/Amphibolis_fixed_SOS3_40588.result/Amphibolis_fixed_SOS3_40588_unrelaxed_rank_1_model_4.pdb')
posi_SOS3_alpha <- read.pdb('data//SOS3_OG0000189/6P_australis_SOS3_dcfd4.result/6P_australis_SOS3_dcfd4_unrelaxed_rank_1_model_1.pdb')
rice_SOS3_alpha <- read.pdb('data//SOS3_OG0000189/LOC_Os05g45810.1_colabfold_test_77dbc.result/test_77dbc_unrelaxed_rank_1_model_4.pdb')
```

@@

```{r}
m_glimpse(rice_SOS3_alpha, outline = FALSE) %>% 
  m_spin()
```

```{r}
m_glimpse(posi_SOS3_alpha, outline = FALSE) %>% 
  m_spin()
```

```{r}
m1 <- r3dmol() %>%
  m_add_model(data = 'data//SOS3_OG0000189/6P_australis_SOS3_dcfd4.result/6P_australis_SOS3_dcfd4_unrelaxed_rank_1_model_1.pdb', format = "pdb") %>% 
    m_zoom_to() %>% 
    m_set_style(style = m_style_cartoon(color = "spectrum"))

m2 <- r3dmol() %>%
  m_add_model(data = 'data//SOS3_OG0000189/Amphibolis_fixed_SOS3_40588.result/Amphibolis_fixed_SOS3_40588_unrelaxed_rank_1_model_4.pdb', format = "pdb") %>%
  m_zoom_to() %>% 
  m_set_style(style = m_style_cartoon(color = "spectrum"))

m3 <- r3dmol() %>%
  m_add_model(data = m_fetch_pdb('1v1f'), format = "pdb") %>%
  m_zoom_to() %>% 
  m_set_style(style = m_style_cartoon(color = "spectrum"))

m4 <- r3dmol() %>%
    m_add_model(data = "data//SOS3_OG0000189/LOC_Os05g45810.1_colabfold_test_77dbc.result/test_77dbc_unrelaxed_rank_1_model_4.pdb", format = "pdb") %>%
    m_zoom_to() %>% 
  m_set_style(style = m_style_cartoon(color = "spectrum"))

m_grid(
  viewer = list(m1, m2, m3, m4),
  rows = 2,
  cols = 2,
  control_all = TRUE,
  viewer_config = m_viewer_spec(
    backgroundColor = "lightblue"
  )
)
```

Let's compare these properly

```{r}
files <- c('data//SOS3_OG0000189/Amphibolis_fixed_SOS3_40588.result/Amphibolis_fixed_SOS3_40588_unrelaxed_rank_1_model_4.pdb','data//SOS3_OG0000189/6P_australis_SOS3_dcfd4.result/6P_australis_SOS3_dcfd4_unrelaxed_rank_1_model_1.pdb')
pdbs <- pdbaln(files, exefile='msa')
#xyz <- pdbfit( posi_SOS3_alpha, rice_SOS3_alpha, core.inds )
```

```{r}
core <- core.find(pdbs)
col=rep("black", length(core$volume))
col[core$volume<2]="pink"; col[core$volume<1]="red"
plot(core, col=col)
core.inds <- print(core, vol=1.0)
```

```{r}
xyz <- pdbfit( pdbs, core.inds, outpath = 'output/quick_fit.pdb' )
rd <- rmsd(xyz)
hist(rd, breaks=40, xlab="RMSD (Å)", main="Histogram of RMSD")
```

```{r}
gaps.xyz2 <- gap.inspect(pdbs$xyz[c(1,2), ])
a.xyz <- pdbs$xyz[1, gaps.xyz2$f.inds]
b.xyz <- pdbs$xyz[2, gaps.xyz2$f.inds]
a <- torsion.xyz(a.xyz, atm.inc=1)
b <- torsion.xyz(b.xyz, atm.inc=1)
d.ab <- wrap.tor(a-b)
d.ab[is.na(d.ab)] <- 0
plot.bio3d(abs(d.ab), typ="h", xlab="Residue No.", 
           ylab = "Difference Angle")
```

MUCH better.
```{r}
a <- dm.xyz(a.xyz)
b <- dm.xyz(b.xyz)

plot.dmat( (a - b), nlevels=10, grid.col="gray", xlab="1tag", ylab="1tnd")
```

```{r}
gaps.pos <- gap.inspect(pdbs$xyz)
pc.xray <- pca.xyz(xyz[, gaps.pos$f.inds])
pc.xray
plot(pc.xray)
```
